A Bayesian approach to burial networks to infer social changes in northeastern Taiwan during the European colonization period

### 2021-01-16 analysis/paper/paper.Rmd
update cross referencing and adjust table cell size

library(flextable)
# add column labels
ft <- flextable(posterior_esti_two_phases) %>% 
  set_header_labels(mean_pre = "pre-Euorpean", median_pre = "pre-Euorpean", 
                    `2.5%_pre` = "pre-Euorpean", `97.5%_pre` = "pre-Euorpean",
                    mean_post = "post-Euorpean", median_post = "post-Euorpean", 
                    `2.5%_post` = "post-Euorpean", `97.5%_post` = "post-Euorpean") %>%
  merge_at(i = 1, j = 2:5, part = "header") %>% 
  merge_at(i = 1, j = 6:9, part = "header") %>% 
  add_header_row(values = c("", "mean", "median", "2.5%", "97.5%",
                            "mean", "median", "2.5%", "97.5%"), top = FALSE ) %>% 
  set_caption("Estimated posterior means, medians, and 95% credible intervals for each network parameter of two models.") 
ft
```

@@

<!--archaeological implication based on the results-->
The covariants for both networks, before and after the European presence, provide further information to give insights into how specific elements of the archaeological record relate to the formation of networks (Table \@ref(tab:xxx)). Our covariants were age, sex, ritual pottery, and a wealth index based on the value of grave goods. The pre-European network shows that burials with pottery as ritual vessels tend to be tied. On the other hand, in the post-European network ties tend to be between burials within the same level of wealth. Moreover, in the post-European network, burials with ritual vessels or same sex tend not to be tied. This illustrates that different social and economic mechanisms determined relations between burials for the two periods. Before European arrival, ritual behaviors seem to have been important status indicators, relative to the use of prestige goods. After European presence was established, status indicators shifted from ritual to wealth differences and sex is not associated with status. Physical distance between burials did not correlate to network formation for either period. This means geographical proximity, implying some kinship association, is not a factor for sharing similar goods between burials. This may suggest that the use of burial goods is more individual-oriented instead of kinship-based. In addition, demographic information, such as age and sex, do not show any correlations with network formation for the pre-European network and only sex shows small effect for the post European network. This may be due to the unavailability of age and sex values for many burials in our sample.

>>>>

library(flextable)
# add column labels
ft <- flextable(posterior_esti_two_phases) %>% 
  set_header_labels(mean_pre = "pre-Euorpean", median_pre = "pre-Euorpean", 
                    `2.5%_pre` = "pre-Euorpean", `97.5%_pre` = "pre-Euorpean",
                    mean_post = "post-Euorpean", median_post = "post-Euorpean", 
                    `2.5%_post` = "post-Euorpean", `97.5%_post` = "post-Euorpean") %>%
  merge_at(i = 1, j = 2:5, part = "header") %>% 
  merge_at(i = 1, j = 6:9, part = "header") %>% 
  add_header_row(values = c("", "mean", "median", "2.5%", "97.5%",
                            "mean", "median", "2.5%", "97.5%"), top = FALSE ) %>% 
  align(j = 2:9, align = "right", part = "header") %>% 
  align(i = 1, align = "center", part = "header") %>% 
  width(j = ~ parameter, width = 1.3) %>% 
  width(j = 2:9, width = 0.65) %>% 
  set_caption("Estimated posterior means, medians, and 95% credible intervals for each network parameter of two models.")
ft
```

@@

<!--archaeological implication based on the results-->
The covariants for both networks, before and after the European presence, provide further information to give insights into how specific elements of the archaeological record relate to the formation of networks (Table \@ref(tab:table-posterior-stats)). Our covariants were age, sex, ritual pottery, and a wealth index based on the value of grave goods. The pre-European network shows that burials with pottery as ritual vessels tend to be tied. On the other hand, in the post-European network ties tend to be between burials within the same level of wealth. Moreover, in the post-European network, burials with ritual vessels or same sex tend not to be tied. This illustrates that different social and economic mechanisms determined relations between burials for the two periods. Before European arrival, ritual behaviors seem to have been important status indicators, relative to the use of prestige goods. After European presence was established, status indicators shifted from ritual to wealth differences and sex is not associated with status. Physical distance between burials did not correlate to network formation for either period. This means geographical proximity, implying some kinship association, is not a factor for sharing similar goods between burials. This may suggest that the use of burial goods is more individual-oriented instead of kinship-based. In addition, demographic information, such as age and sex, do not show any correlations with network formation for the pre-European network and only sex shows small effect for the post European network. This may be due to the unavailability of age and sex values for many burials in our sample.
